The Astropy Project:

### 2017-09-29 main.tex
wrapping

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major \astropy\ principles not mentioned in the first paper, the core v2.0 package, and infrastructure in \astropy\ project to support development in \python.
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
    \item Use \escapecmd{\astropypkg} for the astropy package, \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not ``Python''
    \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
    \item If your subpackage was not included, then please a further description of the sub-package on level with what was in the first paper, and highlight any major features in it.   Typically length should be equivalent to one column
    \item Please make sure you are logged into Overleaf or pushing a commit with your information to be able to track the contributors to the paper.

>>>>

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major
        \astropy\ principles not mentioned in the first paper, the core v2.0
        package, and infrastructure in \astropy\ project to support development
        in \python.
    \item We don't plan on including code in this paper, but if you think you
        will need to include code in your section, please add it to a separate
        Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
        not ``Figure''
    \item Use \escapecmd{\astropypkg} for the astropy package,
        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
        ``Python''
    \item If your subpackage was included in Paper I, then please just include a
        note on what the package does, a reference to paper I, and any new major
        updates to your package
    \item If your subpackage was not included, then please a further description
        of the sub-package on level with what was in the first paper, and
        highlight any major features in it. Typical length should be
        equivalent to one column.
    \item Please make sure you are logged into Overleaf or pushing a commit with
        your information to be able to track the contributors to the paper.
